Variance reduction for Markov chains via martingale representations

### 2020-04-13 aap/Revision/vr-mcmc-revision-new-new.tex
update vr-mcmc-revision-new-new.tex

$\bar a_{r,k}(y)=\mathsf{E}\left[f(X^y_{r})\phi_k\left(\xi_{1}\right)\right]$, $r, k\in \mathbb{N}$.

@@

Let $q\geq l, k\in \nset$. Then the coefficients \(a_{q,l,k}(x)\) in \eqref{eq:coeff_mart}  can be alternatively represented as

@@

In the case $\Phi_l=\Phi$ in \eqref{eq:ula_new} for all $l\geq 1,$ we have

>>>>

\label{eq:definition-bar-a-0}
\bar a_{r,k}(y)=\mathsf{E}\left[f(X^y_{r})\phi_k\left(\xi_{1}\right)\right] \,, \text{for $r, k\in \mathbb{N}$.}

@@

Let $q\geq l, k\in \nset$. Then the coefficients \(a_{q,l,k}\) in \eqref{eq:coeff_mart}  can be alternatively represented as

@@

In the homogeneous case $\Phi_l=\Phi$, the coefficients $(\bar{a}_{r,k})$ in \eqref{eq:definition-bar-a-0} are given respectively  for all $l\geq 1,$ by
